---
title: "Non-Insured"
author: "Zahra N."
date: "10/28/2016"
output: html_document
---
i imported the xls to xlsx by google sheet. 
```{r}
Path <- "~/Documents/R Programming/Census"
setwd(Path)
getwd()
install.packages("openxlsx")
library(openxlsx)
abc<-read.xlsx("spreadsheet.xlsx")
```
get ride of two first rows:
```{r}
abc<- abc[-c(1,2),]
```
there are couple of columns that i want to get ride of too
```{r}
abc <-abc[,-c(9:12)]
```
and how to remove those "................"  infront of each state? 
after several time try dot dot dot... i realized the "."" that is used in this table part of them is different from regualr dot.
So I had to copy it from the table by view(abc) and replace it with "". 
```{r}
abc$State <- gsub("…","", abc$State, fixed = TRUE)
abc$State <- gsub(".","", abc$State, fixed = TRUE)
head(abc, 5)
str(abc$State)
abc$State
```
removing +Y into Y
```{r}
abc$`Medicaid.Expansion.State?.Yes.(Y).or.No.(N)1` <-gsub("\\+","",abc$`Medicaid.Expansion.State?.Yes.(Y).or.No.(N)1`)
```
str(abc)
charachter to numertic
```{r}
abc$`2013.Uninsured` <- as.numeric(abc$`2013.Uninsured`)
abc$`2014.Uninsured` <- as.numeric(abc$`2014.Uninsured`)
abc$`2015.Uninsured` <- as.numeric(abc$`2015.Uninsured`)
abc$X4 <- as.numeric(abc$X4)
str(abc)
```

Pie Chart
```{r}
pie(abc$`2013.Uninsured`, labels=abc$State) 

```


![pie Chart] (~/Users/zahra/Documents/R Programming/Census/Pie Chart.png)

```
![pie Chart] (~/Users/zahra/Documents/R Programming/Census/Pie Chart.png)

Creating map
```{r}
install.packages("maps")
library(maps)
install.packages(ggplot2)
library(ggplot2)
install.packages("data.table")
library(data.table)
```

state_map <- map_data('state')
head(state_map)



all_states <- abc$State
setkey(all_states, region)
uninsured <- abc$'2013.Uninsured'
setkey(uninsured,stateName)
























i!
