---
title: "Non-Insured"
author: "Zahra N."
date: "10/28/2016"
output: html_document
---
```{r load packages}
require(openxlsx)
require(maps)
require(ggplot2)
require(mapproj)


```

i imported the xls to xlsx by google sheet. 
```{r import data}
abc<-read.xlsx("~/Documents/R Programming/Census/spreadsheet.xlsx")
```
get ride of two first rows:
```{r}
abc<- abc[-c(1,2),]
```
there are couple of columns that i want to get ride of too
```{r}
abc <-abc[,-c(9:12)]
abc <-abc[,-c(2:6)]
abc <-abc[,-c(3)]
```
and how to remove those "................"  infront of each state? 
after several time try dot dot dot... i realized the "."" that is used in this table part of them is different from regualr dot.
So I had to copy it from the table by view(abc) and replace it with "". 
```{r}
abc$State <- gsub("…","", abc$State, fixed = TRUE)
abc$State <- gsub(".","", abc$State, fixed = TRUE)

```

charachter to numertic
```{r}
abc$`2015.Uninsured` <- as.numeric(abc$`2015.Uninsured`)

```
changing the name
```{r}
colnames(abc) [2]<- "Uninsured"
```
Creating the map
```{r}
abc$region <- tolower(abc$State)
states <- map_data("state")
map.df <- merge(states,abc, by="region", all.x=T)
map.df <- map.df[order(map.df$order),]
head(map.df)
ggplot(map.df, aes(x=long,y=lat,group=group))+
  geom_polygon(aes(fill=Uninsured))+
  geom_path()+ 
  scale_fill_gradientn(colours=rev(heat.colors(30)))+
  coord_map()


```















