---
title: "Non-Insured"
author: "Zahra N."
date: "10/28/2016"
output: html_document
---
i imported the xls to xlsx by google sheet. 
```{r}
Path <- "~/Documents/R Programming/Census"
setwd(Path)
getwd()
install.packages("openxlsx")
library(openxlsx)
abc<-read.xlsx("spreadsheet.xlsx")
```
get ride of two first rows:
```{r}
abc<- abc[-c(1,2),]
```
there are couple of columns that i want to get ride of too
```{r}
abc <-abc[,-c(9:12)]
abc <-abc[,-c(2:6)]
abc <-abc[,-c(3)]
head(abc)
```
and how to remove those "................"  infront of each state? 
after several time try dot dot dot... i realized the "."" that is used in this table part of them is different from regualr dot.
So I had to copy it from the table by view(abc) and replace it with "". 
```{r}
abc$State <- gsub("…","", abc$State, fixed = TRUE)
abc$State <- gsub(".","", abc$State, fixed = TRUE)
head(abc, 5)
str(abc$State)

```

charachter to numertic
```{r}
abc$`2015.Uninsured` <- as.numeric(abc$`2015.Uninsured`)
str(abc)
```
changing the name
```{r}
colnames(abc) [2]<- "Uninsured"
head(abc)
```
Creating the map
```{r}
install.packages("maps")
library(maps)
install.packages(ggplot2)
library(ggplot2)
install.packages('mapproj')
library(mapproj)
abc$region <- tolower(abc$State)
head(abc,15)
states <- map_data("state")
map.df <- merge(states,abc, by="region", all.x=T)
map.df <- map.df[order(map.df$order),]
head(map.df)
ggplot(map.df, aes(x=long,y=lat,group=group))+
  geom_polygon(aes(fill=Uninsured))+
  geom_path()+ 
  scale_fill_gradientn(colours=rev(heat.colors(30)))+
  coord_map()


```







all_states <- abc$State
setkey(all_states, region)
uninsured <- abc$'2013.Uninsured'
setkey(uninsured,stateName)
?map
map()
map('usa')
map_data("state")
state_map <- map_data('state')
head(state_map)

head(abc)
all_states <- data.table(map_data('State'))
head(all_states)
abc$region <- abc$State

setkey(all_states,region)
abc <- data.table(Prison)
setkey(Prison,stateName)


tolower(abc$State)
gsub('(.*)', '\\L\\1', state.name, perl = TRUE)
















all_states <- map_data("state")
all_states
head(all_states)
abc$region <- abc$State
Total <- merge(all_states, abc, by="region")
head(Total)
Total <- Total[Total$region!="district of columbia",]























